\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-02 doc/paper.tex
doc/paper.tex: refer to Sec:SpecGenStruct in section "Adapting C++ code"

Since the current implementation of \fs does not (yet)
produce a spectrum generator spanning multiple models,
one needs to write the matching object
% in \figref{fig:class structure for tower}
as well as gluing codes by hand to build such a program.
Nevertheless, the clean object structure eases this job.

>>>>

Since the current implementation of \fs does not (yet)
produce a spectrum generator spanning multiple models,
one needs to write the matching object
% in \figref{fig:class structure for tower}
as well as gluing codes by hand to build such a program.
Nevertheless, the clean object structure eases this job.
One can author nearly all the components of a multi-model spectrum generator
by making a straightforward extension
to each corresponding single-model counterpart
for one of the models forming the tower.
For this, it should help to have working knowledge about the basic structure
of a spectrum generator, set out in \secref{Sec:SpecGenStruct}.
Obviously, this tip does not work for the matching class,
which has no analogue in a single-model case.
